Bayesian Data Analysis, Rough Draft

### 2023-12-01 Lahman Analysis/Formal Analysis/Draft1.qmd
Standardization of FF notation and mine

$$
\begin{align}
h_{ij}|\pi_{ij}&\sim Binomial(ab_{ij},\pi_{ij})\\
\\
logit(\frac{\pi_{ij}}{1-\pi_{ij}})&=x_{ij}\beta_{i}+\theta_i+\delta_j
+\xi_p
\end{align}
$$

@@

$$
\begin{align}
\theta_i&\sim Normal(\mu_d,\sigma^2_{d_i}), d\in \{1...14\}, i\in\{1,...,3735\}\\
\\
\mu_d&\sim Normal(-2.5,var=1), d_i\in\{1,...,14\}\\
\\
\sigma^2_{d_i}&\sim Gamma(3,3), d_i\in\{1,...14\} \\
\\
\delta_j&\sim Normal(-2.5, var=4),j\in \{1,...,138\}\\
\\
\xi_p&\sim Normal(-2.5, var=4), p\in \{1,...,222\}\\
\end{align}
$$

@@

$$
\begin{align}
HR_{ni} &\sim Binomial(AB_{ni},\pi_{ni})\\
logit(\frac{\pi_{ni}}{1-\pi_{ni}}) &= \alpha_{n}+\beta_h+\eta_h+\delta_p+\xi_i
\end{align}
$$

>>>>

$$
\begin{align}
HR_{nip}|\pi_{nip}&\sim Binomial(AB_{nip},\pi_{nip})\\
\\
logit(\frac{\pi_{nip}}{1-\pi_{nip}})&=\beta_{n1}\cdot Age_{ni}+\beta_{n2}\cdot(Age_{ni})^2+\beta_{n3}\cdot(Age_{ni})^3+\beta_{n4}\cdot(Age_{ni})^4+\alpha_n+\delta_i
+\xi_p
\end{align}
$$

@@

$$
\begin{align}
\alpha_n&\sim Normal(\mu_{d_n},\sigma^2_{d_n}), d\in \{1...14\}, n\in\{1,...,3735\}\\
\\
\mu_d&\sim Normal(-2.5,1), d\in\{1,...,14\}\\
\\
\sigma^2_{d}&\sim Gamma(3,3), d\in\{1,...14\} \\
\\
\delta_i&\sim Normal(-2.5, 2),i\in \{1,...,138\}\\
\\
\xi_p&\sim Normal(-2.5, 2), p\in \{1,...,222\}\\
\end{align}
$$

@@

$$
\begin{align}
HR_{nip} &\sim Binomial(AB_{nip},\pi_{nip})\\
\log(\pi_{nip}) &= \alpha_{n}+\beta_n\cdot (Age_{ni}-30)+\eta_n\cdot (Age_{ni}-30)^2+\delta_p+\xi_i
\end{align}
$$
